\Large \bf Uncovering Bugs in Distributed Storage Systems\\during Testing (not in Production!)

### 2016-01-25 vnext.tex
added new reference

Azure Storage vNext is the next generation storage system currently being developed for Microsoft Azure, where the primary design target is to scale the storage capacity by more than 100$\times$. Similar to the current system, vNext employs containers, called \emph{extents}, to store data. Extents can be several gigabytes each, consisting of many data blocks, and are replicated over multiple \emph{Extent Nodes} (ENs). However, in contrast to the current system, which uses a Paxos-based, centralized mapping from extents to ENs, vNext achieves scalability by using a \emph{distributed mapping}. In vNext, extents are divided into partitions, with each partition managed by a lightweight \emph{Extent Manager} (ExtMgr). This partitioning is illustrated in Figure~\ref{fig:vnext}.

>>>>

Azure Storage vNext is the next generation storage system currently being developed for Microsoft Azure, where the primary design target is to scale the storage capacity by more than 100$\times$. Similar to the current system, vNext employs containers, called \emph{extents}, to store data. Extents can be several gigabytes each, consisting of many data blocks, and are replicated over multiple \emph{Extent Nodes} (ENs). However, in contrast to the current system, which uses a Paxos-based, centralized mapping from extents to ENs~\cite{calder2011windows}, vNext achieves scalability by using a \emph{distributed mapping}. In vNext, extents are divided into partitions, with each partition managed by a lightweight \emph{Extent Manager} (ExtMgr). This partitioning is illustrated in Figure~\ref{fig:vnext}.
